---
title: "codeReviewR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Known limitations
- for loops
    - at all
    - convert all '<-' to '=' exception '<<-'
- sf objects (needs to test)
- automate lists of items captured 
    - order_inputs
    - order_outputs

```{r}
library(tidyverse)

file_name <- "test.Rmd"

get_file <- read_file(file_name)

make_edits <-
    get_file %>% 
    str_replace_all(" +"," ") %>% 
    str_replace_all("\\n(#.*)\\r", "") %>% #single line comments
    str_replace_all("(\\%\\>\\%|,)( #.*)", "\\1 ") %>% #inline comments
    str_replace_all("(\\<\\-)[ \r\n]+", "\\1 ") %>% #assignments
    str_replace_all("(,)[ \r\n]+", "\\1 ") %>% #commas
    #str_replace_all("\"[^\"]+\",?", '""') %>% #quoted text + comma
    #str_replace_all(",\\s*\\)", ")") %>% #remove leading comma at end ex: (obj,)
    str_replace_all("(\\%\\>\\%)[ \r\n]+", "\\1 ") %>% #dplyr pipe
    str_replace_all("(\\+)[ \r\n]+", "\\1 ") %>% #ggplot pipe
    str_replace_all("([\\{\\(]+)[ \r\n]+", "\\1 ") %>% #open bracket/parens
    str_replace_all("[ \r\n]+([\\}\\)]+)", "\\1 ") #move close bracket/parens up


n_open <- 0
output <- ""

for(i in 1:nchar(make_edits)){
        x <- str_sub(make_edits, i, i)
        if(x == '{'){ n_open <- n_open + 1}
        if(x == '}'){ n_open <- n_open - 1}
        if(n_open > 0 && str_detect(x, "[\r\n]")){ 
            x = ";"
        }
        output <- paste0(output, x)
}

out_file <-
    tibble(text = read_lines(str_replace_all(output, ";+", ";"))) %>% 
    filter(str_detect(text, "<-|^library|^for\\("))

file_details <-
    out_file %>% 
    mutate(line = row_number()) %>% 
    mutate(creation = ifelse(str_detect(text, "\\<\\-"),
                             str_replace(text, "(.*) \\<\\-.*", "is(\\1)"),
                             NA),
           is = "") %>% 
    #unnest(verbs2 = str_split(verbs, ",")) %>% 
    group_by(line) %>% 
    mutate(ord = row_number()) %>% 
    ungroup()

file_details

make_file <- 
    paste0(out_file$text, collapse = "\r\n") %>% 
    paste("\r\n")
    
write_file(make_file, "output.R")
```
  

```{r}
parse_it <- function(get_line){
    #run the line
        eval(parse(text = file_details$text[get_line]), envir = .GlobalEnv)

    #identify functions
        get_fx_pkg <-
            tibble(pkg = search()) %>% 
            filter(str_detect(pkg, "package")) %>% 
            rowwise() %>% 
            mutate(fx = list(as.character(ls.str(pkg)))) %>% 
            ungroup() %>% 
            unnest(fx) %>% 
            filter(str_detect(tolower(fx), "^[a-z]")) %>% 
            distinct(fx) %>% 
            .$fx #mutate(src = "pkg")
        
        get_fx_local <-
            tibble(fx = list(as.character(lsf.str(search())))) %>% 
            unnest(fx) %>% 
            .$fx #mutate(src = "local")
        
        #get_fx <- c(get_fx_pkg, get_fx_local)
        
        get_objects <-
            tibble(obj = list(as.character(ls.str(search())))) %>% 
            unnest(obj) %>% 
            filter(!obj %in% get_fx_local) %>% 
            .$obj
        
    #make dataframe of found functions
        local_fx_list <- paste0(paste0(get_fx_local,'\\('), collapse = "|")

        fx_found <- str_detect(file_details$text[get_line], local_fx_list)

        if(fx_found){
            fx_df <-
                tibble(step = get_line,
                       text = (str_extract_all(file_details$text[get_line], local_fx_list)),
                       final = "local function") %>%
                rowwise() %>% 
                unnest(text) %>% 
                mutate(text = str_replace(text, "\\(", ""))
        }

    #pattern to identify single column manipulation
        assignment_pattern <- "^\\w+\\$\\w+ \\<-" #ex: "mpg$cyl <- 2"
        
    #single column
    if(str_detect(file_details$text[get_line], assignment_pattern)){
            file_details$is[get_line] <<- "single column"
    
            df <-
                tibble(step = get_line,
                       text = str_extract(file_details$text[get_line], "\\w+\\$\\w+"),
                       final = "single column manipulation") %>% 
                rbind(
                    tibble(step = get_line,
                           text = str_extract(file_details$text[get_line], "\\w+"),
                           final = "obj dependency")
                    )

    #loops            
    } else if(str_detect(file_details$text[get_line], "^for|^while")){
        file_details$is[get_line] <<- "loop"
        
        df <-
            tibble(step = get_line,
                   text = paste(str_extract(file_details$text[get_line], '\\w+'), "loop"),
                   final = "loop")
    
    #libraries            
    } else if(str_detect(file_details$text[get_line], "^library")){
        file_details$is[get_line] <<- "library"
        
        df <-
            tibble(step = get_line,
                   text = file_details$text[get_line],
                   final = "load library")
        
    #functions            
    } else if(str_detect(file_details$text[get_line], "\\<- function\\(")){
        file_details$is[get_line] <<- "function"

        df <-
            tibble(step = get_line,
                   text = str_extract(file_details$text[get_line], "\\w+"),
                   final = "function")

    #main funciton        
    } else {
        #get_line = 2
        get_type <- 
            #file_details$creation is an 'is()' statement
            eval(parse(text = file_details$creation[get_line])) 
        
        x <- 
            get_type %>% 
            paste0(collapse = "|")
        
        file_details$is[get_line] <<-
            case_when(str_detect(x, "^list") ~ "list",
                      str_detect(x, "tbl|DT") ~ "table",
                      str_detect(x, "vector|POSIX") ~ "constant",
                      TRUE ~ as.character(get_type[1]))
        
        df <-
            getParseData(
                parse(text = file_details$text[get_line])
            ) %>% 
            as.tibble() %>%
            mutate(step = get_line) %>% 
            select(step, parent:text) %>% 
            filter(terminal == T,
                   str_detect(token, "SYMBOL")) %>% 
            filter((!str_detect(token, "SYMBOL_FUNCTION_CALL") | text %in% get_fx_local)) %>% 
            #group_by(text) %>% mutate(first = first(token)) %>% ungroup() %>% 
            mutate(final = 
                       case_when(row_number() == 1 ~ "new object",
                                 str_detect(token, "SUB") ~ "new column",
                                 text %in% get_fx_pkg ~ "from libary",
                                 text %in% get_fx_local ~ "local function",
                                 #ls("package:datasets")
                                 text %in% get_objects ~ "obj dependency",
                                 TRUE ~ "")) %>% 
            filter(final != "") %>% 
            select(step, text, final)%>%
            distinct()
    }

    if(fx_found){ df <- rbind(df, fx_df) }
        
    return(df)
}

```

```{r}
parse_df <-
    parse_it(1)

for(i in 2:nrow(file_details)){
    parse_df <- rbind(parse_df, parse_it(i))
    print(i)
}

```

```{r}
prep_plot <-
    parse_df %>% 
    mutate(obj = ifelse(str_detect(final, "obj"), "obj", final),
           plot = ifelse(str_detect(final, "lib|obj|func|loop"), "plot", "detail")) %>% 
    group_by(step) %>% 
    mutate(dir = ifelse(row_number() == 1, "output", "input")) %>% 
    ungroup()

prep_plot

get_outputs <-
    prep_plot %>% 
    filter(dir == "output") %>%
    select(step, output = text, create = obj)

get_inputs <-
    prep_plot %>% 
    filter(dir == "input",
           plot == "plot") %>% 
    select(step, input = text, type = obj) %>% 
    left_join(get_outputs %>% select(input = output, input_step = step)) %>% 
    left_join(file_details %>% select(input_step = line, input_detail = text, input_is = is))
    

order_outputs <- 
    c("list", "loop", "constant", "function", "table", "single column", "unused", "library") %>%
    .[. %in% file_details$is]

order_inputs <- 
    as.character(c("list", "loop", "constant", "function", "table", "unused")) %>%
    .[. %in% get_inputs$input_is]


final_plot <-
    get_outputs %>% 
    full_join(get_inputs, by = "step") %>% 
    left_join(file_details %>% select(step = line, detail = text, is)) %>% 
    mutate(is = factor(is, ordered = T) %>% fct_relevel(order_outputs),
           input_is = factor(input_is, ordered = T) %>% fct_relevel(order_inputs)) %>% 
    mutate(is_color = 
               case_when(is == "library" ~ "khaki1",
                         is == "constant" ~ "skyblue1",
                         is == "table" ~ "turquoise3",
                         is == "function" ~ "violet",
                         is == "single column" ~ "chocolate1",
                         is == "loop" ~ "grey85",
                         is == "list" ~ "grey85",
                         TRUE ~ "grey85")) %>% 
    mutate(input_is_color = 
               case_when(input_is == "library" ~ "khaki1",
                         input_is == "constant" ~ "skyblue1",
                         input_is == "table" ~ "turquoise3",
                         input_is == "function" ~ "violet",
                         input_is == "single column" ~ "chocolate1",
                         input_is == "loop" ~ "grey85",
                         input_is == "list" ~ "grey85",
                         TRUE ~ "grey85"))
        
get_curve <-
    final_plot %>% 
    filter(step != input_step) %>% 
    mutate(curve = ifelse((input_is == "table"), "up", "down"))

#p <-
ggplot(final_plot, aes(x = (step), y = is)) +
    #geom_count() +
    #geom_segment(aes(xend = step, yend = order_outputs[1], color = is_color), size = 10, alpha = .2) +
    geom_curve(data = filter(get_curve, curve == "up"),
               aes(x = (input_step), y = input_is, 
                   xend = step, yend = is,
                   color = input_is_color),
               curvature = -0.25,
               #arrow = arrow(length = unit(0.4,"cm"), type = "closed"),
               #arrow = arrow(length = unit(0.2, "cm"), type = "open"),
               size = 1) +
    geom_curve(data = filter(get_curve, curve == "down"),
               aes(x = (input_step), y = input_is, 
                   xend = step, yend = is,
                   color = input_is_color),
               curvature = 0.25,
               #arrow = arrow(length = unit(0.4,"cm"), type = "closed"),
               #arrow = arrow(length = unit(0.2, "cm"), type = "open"),
               size = 1) +
    geom_label(data = distinct(final_plot, output, is, step, is_color),
               aes(label = output, fill = is_color),
               #nudge_x = -0.1, 
               nudge_y = 0.1, #alpha = 0.9,
               label.padding = unit(0.4, "lines")) +
    #geom_label(aes(label = output, color = is), vjust = 0.1, hjust = -0.1) +
    #expand_limits(x = c(-0.5, nrow(file_details) + 2)) +
    #expand = expand_scale(mult = c(0, .1)))
    scale_color_identity() +
    scale_fill_identity() +
    scale_y_discrete(limits = order_outputs) +
    scale_x_continuous(limits = c(0.5, nrow(file_details) * 1.1), 
                       breaks = seq_len(nrow(file_details)),
                       labels = seq_len(nrow(file_details))) +
    labs(title = paste("Analyis of", file_name), 
         subtitle = paste(lubridate::today(), "\n"),
         x = "step",
         y = "") +
    theme_classic()
```

